### 2016-06-14 hoist.tex
Adding sections
partition

@@

\section{Hoisting scalars}
Scalars are the easiest to hoist because we do not have to analyze for mem-refs. As long as all the
operands are available (which in SSA form we do, or may be there are chained dependencies), the scalar can
be hoisted. Care must be taken in case of hoisting scalars too far, as that may increase register pressure
and result in spills. For example hoisting a scalar past a call. In that case the call may result in
save and restore of the register the scalar may be defined to. In our current implementation
we do not hoist scalars past a call. Another way to mitigate this problem would be to
reinstantiate (rematerialize) the computation after a call (may be as a different pass).

@@

Bottom up:
Sort the basic blocks of potentially redundant computations based on DFS-in numbers.
Then start evaluating the safety checks for first two, if good then move to second one. That way we can even
partially hoist computations should we find that we cannot remove all the redundant computations.

@@

>>>>

\section{Introduction}

\section{Global Value Numbering}
\section{Code Hoisting}
Code hoisting does not remove redundancies by itself but it enables removal of redundancies by other passes.
e.g., Enable inlining.
\section{Related Work}

\section{Cost models}
\subsection{In the presence of calls}
\subsection{Hoisting too far away}

\section{Comparative analysis of different approaches to hoisting}
\subsection{Optimistic approach}
Collect GVN of all the instructions in the beginning.
\subsection{Pessimistic approach}
Start from a branch.

@@

\section{Hoisting scalars}
Scalars are the easiest to hoist because we do not have to analyze for mem-refs. As long as all the
operands are available (which in SSA form we do, or may be there are chained dependencies), the scalar can
be hoisted. Care must be taken in case of hoisting scalars too far, as that may increase register pressure
and result in spills. For example hoisting a scalar past a call. In that case the call may result in
save and restore of the register the scalar may be defined to. In our current implementation
we do not hoist scalars past a call. Another way to mitigate this problem is be to
reinstantiate (rematerialize) the computation after a call (may be as a different pass).

@@

Bottom up:
Sort the basic blocks of potentially redundant computations based on DFS-in numbers.
TODO: Explain why sorting by DFS-in numbers.
Then start evaluating the safety checks for first two, if good then move to second one. That way we can even
partially hoist computations should we find that we cannot remove all the redundant computations.

@@

\section{Partition the list of hoisting candidates to maximize hoisting}
The set of candidates are sorted in the order of their DFS-in numbers. So that candidates close to
each other in the list are also closer (??) in the CFG.

In the case where all the candidates cannot be hoisted at a common hoist point because of:
\begin{enumerate}
\item Safety conditions are not met.
\item Live range would increase too much.
\end{enumerate}

We partition the list at the point where the above mentioned checks fail.
TODO: Put an example to illustrate the point.
